Algomusicology, ????, Profit

### 2016-04-03 paper.tex
Fill out references.

The South Park Underpants Gnomes are renowned for their business plan:
\begin{enumerate}
    \item Collect underpants
    \item ?
    \item Profit
\end{enumerate}

@@

The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig, a music theory library,
\footnote{Leipzig provides ways of describing notes in terms of higher order concepts like chords and scales.}
and Midje, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
which asserts that expression evaluates to result.}

\section{Air on the {\textbackslash}G String}
Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
evaluates to a sequence of $10^{15}$ uppercase G characters:

@@

@@

David Meredith has used Kolmogorov complexity to compare the quality of musical analyses. The theory goes that the
more concise the algorithmic description of a piece, the better the musical model.

@@

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.

@@

In Carl Sagan's novel 'Contact', he imagines that a message to humanity is encoded in the digits of pi. If we design an
appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However, we would encounter
a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want is in there
somewhere, but we don't know where to look.

@@

The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
"a succession of repetitive beats" were played.

The duo Autechre responded with the Anti EP, whose third track 'Flutter', was designed to protest the legislation. Band member
Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
of "repetitive beats".

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a field,
so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})

>>>>

The South Park Underpants Gnomes\cite{Gnomes} are renowned for their business plan:
\begin{enumerate}
    \item Collect underpants
    \item ?
    \item Profit
\end{enumerate}

@@

The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig\cite{Leipzig},
a music theory library,
\footnote{Leipzig provides ways of describing notes in terms of higher order concepts like chords and scales.}
and Midje\cite{Midje}, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
which asserts that expression evaluates to result.}

\section{Air on the {\textbackslash}G String\cite{Air on the G String}}
Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
evaluates to a sequence of $10^{15}$ uppercase G characters:

@@

The insight that the inherent complexity of data can be measured by the length of the computer program needed to express it
originates with Andrey Kolmogorov\cite{On Tables of Random Numbers}. The Kolmogorov complexity of a piece of data is defined
as the length of the shortest program that evaluates to it.

@@

David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
The theory goes that the
more concise the algorithmic description of a piece, the better the musical model.

@@

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges\cite{The Library of Babel}. In his
vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.

@@

In Carl Sagan's novel 'Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
If we design an appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However,
we would encounter a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want
is in there somewhere, but we don't know where to look.

@@

The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
"a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track 'Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
of "repetitive beats".

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a field,
so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."\cite{Joseph Gallivan on pop}

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})
\bibitem{Air on the G String} Bach, Johann Sebastian: Air on the G String
\bibitem{The Library of Babel} Borges, Jorge Luis
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
\bibitem{Leipzig} Ford, Chris: Leipzig
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
\bibitem{Midje} Marick, Brian: Midje
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
\bibitem{Contact} Sagan, Carl: Contact
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines
